---
title: "Flu Shot Learning"
output: html_document
---

## Context

The DrivenData website launched a data competition on [H1N1 and seasonal flu vaccination](https://www.drivendata.org/competitions/66/flu-shot-learning/page/210/). The objective is to predict how likely individuals are to receive their flu vaccines based on data and information collected in a phone survey. 

## Setup
```{r setup, message=FALSE}
knitr::opts_chunk$set(echo = TRUE)
rm(list = ls())
```

```{r packages, message=FALSE}
library(tidyverse)
library(magrittr)
library(cowplot)
library(janitor)
library(mlr)
theme_set(theme_minimal())
```

## Data

Data were downloaded from the [website](https://www.drivendata.org/competitions/66/flu-shot-learning/data/) on April 14th, 2020.

```{r data, message=FALSE}
train_features <- read_csv("~/projects/driven_data/flu_shot/data/raw/training_set_features.csv")
train_labels <- read_csv("~/projects/driven_data/flu_shot/data/raw/training_set_labels.csv")
test_features <- read_csv("~/projects/driven_data/flu_shot/data/raw/test_set_features.csv")
submission_format <- read_csv("~/projects/driven_data/flu_shot/data/raw/submission_format.csv")
```

## Initial exploration

```{r}
dim(train_features)
dim(train_labels)
dim(test_features)
dim(submission_format)
```

From the above we can see that the training datasets have 26707 rows (using the head and tail functions we can see that those rows correspond to respondant_id 0 to 26706) and the test datasets has 26708 rows (respondant_id 26707 to 53414). We can also see that features for both the training and testing datasets include 36 variables and a quick verification with the intersect function confirmed that the variables are the same for the training and testing datasets.
```{r}
intersect(names(train_features), names(test_features))
```

Using the same function we can confirm that the only common variable to the features and labels datasets are the respondant_id: 
```{r}
intersect(names(train_features), names(train_labels))
intersect(names(test_features), names(submission_format))
```

We can therefore join the features and labels of the training datasets resulting in the same number of rows with two additional variables being h1n1_vaccine and seasonal_vaccine (the ones to prdict in the test dataset):
```{r}
train_all <- train_labels %>% left_join(train_features)
dim(train_all)
head(train_all)
```

The [data for this competition comes from the National 2009 H1N1 Flu Survey (NHFS)](https://www.drivendata.org/competitions/66/flu-shot-learning/page/213/). In their own words: 

> The National 2009 H1N1 Flu Survey (NHFS) was sponsored by the National Center for Immunization and Respiratory Diseases (NCIRD) and conducted jointly by NCIRD and the National Center for Health Statistics (NCHS), Centers for Disease Control and Prevention (CDC). The NHFS was a list-assisted random-digit-dialing telephone survey of households, designed to monitor influenza immunization coverage in the 2009-10 season.
> The target population for the NHFS was all persons 6 months or older living in the United States at the time of the interview. Data from the NHFS were used to produce timely estimates of vaccination coverage rates for both the monovalent pH1N1 and trivalent seasonal influenza vaccines.

According to [Google](https://www.google.com/publicdata/explore?ds=kf7tgg1uo9ude_&met_y=population&idim=country:US&hl=en&dl=en) based on U.S. Census Bureau data, the total population in the USA in 209 was approximately 306.8 million. With a training dataset including 26708 respondants (with respondant 0) it therefore represents approximately 0.0087% of the population. Given that the survey was as "list-assisted random-digit-dialing telephone survey of households" in the USA, it is reasonable to consider the sample representative of the whole population.

### Data description

The description for the variables below are from the [DrivenData](https://www.drivendata.org/competitions/66/flu-shot-learning/page/211/) website:

There are two target variables (multilabel problem) and both are binary variables(0 = No; 1 = Yes):

* h1n1_vaccine - Whether respondent received H1N1 flu vaccine.
* seasonal_vaccine - Whether respondent received seasonal flu vaccine.

There are 36 features in this dataset, hence a dataset with 36 columns. The first column respondent_id is a unique and random identifier. The remaining 35 features are described below. For all binary variables: 0 = No; 1 = Yes.

* h1n1_concern - Level of concern about the H1N1 flu.
    - 0 = Not at all concerned; 1 = Not very concerned; 2 = Somewhat concerned; 3 = Very concerned.
* h1n1_knowledge - Level of knowledge about H1N1 flu.
    - 0 = No knowledge; 1 = A little knowledge; 2 = A lot of knowledge.
* behavioral_antiviral_meds - Has taken antiviral medications. (binary)
* behavioral_avoidance - Has avoided close contact with others with flu-like symptoms. (binary)
* behavioral_face_mask - Has bought a face mask. (binary)
* behavioral_wash_hands - Has frequently washed hands or used hand sanitizer. (binary)
* behavioral_large_gatherings - Has reduced time at large gatherings. (binary)
* behavioral_outside_home - Has reduced contact with people outside of own household. (binary)
* behavioral_touch_face - Has avoided touching eyes, nose, or mouth. (binary)
* doctor_recc_h1n1 - H1N1 flu vaccine was recommended by doctor. (binary)
* doctor_recc_seasonal - Seasonal flu vaccine was recommended by doctor. (binary)
* chronic_med_condition - Has any of the following chronic medical conditions: asthma or an other lung condition, diabetes, a heart condition, a kidney condition, sickle cell anemia or other anemia, a neurological or neuromuscular condition, a liver condition, or a weakened immune system caused by a chronic illness or by medicines taken for a chronic illness. (binary)
* child_under_6_months - Has regular close contact with a child under the age of six months. (binary)
* health_worker - Is a healthcare worker. (binary)
* health_insurance - Has health insurance. (binary)
* opinion_h1n1_vacc_effective - Respondent's opinion about H1N1 vaccine effectiveness.
    - 1 = Not at all effective; 2 = Not very effective; 3 = Don't know; 4 = Somewhat effective; 5 = Very effective.
* opinion_h1n1_risk - Respondent's opinion about risk of getting sick with H1N1 flu without vaccine.
    - 1 = Very Low; 2 = Somewhat low; 3 = Don't know; 4 = Somewhat high; 5 = Very high.
* opinion_h1n1_sick_from_vacc - Respondent's worry of getting sick from taking H1N1 vaccine.
    - 1 = Not at all worried; 2 = Not very worried; 3 = Don't know; 4 = Somewhat worried; 5 = Very worried.
* opinion_seas_vacc_effective - Respondent's opinion about seasonal flu vaccine effectiveness.
    - 1 = Not at all effective; 2 = Not very effective; 3 = Don't know; 4 = Somewhat effective; 5 = Very effective.
* opinion_seas_risk - Respondent's opinion about risk of getting sick with seasonal flu without vaccine.
    - 1 = Very Low; 2 = Somewhat low; 3 = Don't know; 4 = Somewhat high; 5 = Very high.
* opinion_seas_sick_from_vacc - Respondent's worry of getting sick from taking seasonal flu vaccine.
    - 1 = Not at all worried; 2 = Not very worried; 3 = Don't know; 4 = Somewhat worried; 5 = Very worried.
* age_group - Age group of respondent.
* education - Self-reported education level.
* race - Race of respondent.
* sex - Sex of respondent.
* income_poverty - Household annual income of respondent with respect to 2008 Census poverty thresholds.
* marital_status - Marital status of respondent.
* rent_or_own - Housing situation of respondent.
* employment_status - Employment status of respondent.
* hhs_geo_region - Respondent's residence using a 10-region geographic classification defined by the U.S. Dept. of Health and Human Services. Values are represented as short random character strings.
* census_msa - Respondent's residence within metropolitan statistical areas (MSA) as defined by the U.S. Census.
* household_adults - Number of other adults in household, top-coded to 3.
* household_children - Number of children in household, top-coded to 3.
* employment_industry - Type of industry respondent is employed in. Values are represented as short random character strings.
* employment_occupation - Type of occupation of respondent. Values are represented as short random character strings.

```{r cleaning, include=FALSE}
train_all <- train_all %>% mutate(
    h1n1_vaccine = as.factor(h1n1_vaccine),
    seasonal_vaccine = as.factor(seasonal_vaccine),
    h1n1_concern = as.factor(h1n1_concern),
    h1n1_knowledge = as.factor(h1n1_knowledge), 
    behavioral_antiviral_meds = as.factor(behavioral_antiviral_meds),
    behavioral_avoidance = as.factor(behavioral_avoidance),
    behavioral_face_mask = as.factor(behavioral_face_mask),
    behavioral_wash_hands = as.factor(behavioral_wash_hands),
    behavioral_large_gatherings = as.factor(behavioral_large_gatherings),
    behavioral_outside_home = as.factor(behavioral_outside_home),
    behavioral_touch_face = as.factor(behavioral_touch_face),
    doctor_recc_h1n1 = as.factor(doctor_recc_h1n1),
    doctor_recc_seasonal = as.factor(doctor_recc_seasonal),
    chronic_med_condition = as.factor(chronic_med_condition),
    child_under_6_months = as.factor(child_under_6_months),
    health_worker = as.factor(health_worker),
    health_insurance = as.factor(health_insurance),
    opinion_h1n1_vacc_effective = as.factor(opinion_h1n1_vacc_effective),
    opinion_h1n1_risk = as.factor(opinion_h1n1_risk),
    opinion_h1n1_sick_from_vacc = as.factor(opinion_h1n1_sick_from_vacc),
    opinion_seas_vacc_effective = as.factor(opinion_seas_vacc_effective),
    opinion_seas_risk = as.factor(opinion_seas_risk),
    opinion_seas_sick_from_vacc = as.factor(opinion_seas_sick_from_vacc),
    age_group = as.factor(age_group),
    education = as.factor(education),
    race = as.factor(race),
    sex = as.factor(sex),
    income_poverty = as.factor(income_poverty),
    marital_status = as.factor(marital_status),
    rent_or_own = as.factor(rent_or_own),
    employment_status = as.factor(employment_status),
    hhs_geo_region = as.factor(hhs_geo_region),
    census_msa = as.factor(census_msa),
    household_adults = as.factor(household_adults),
    household_children = as.factor(household_children),
    employment_industry = as.factor(employment_industry),
    employment_occupation = as.factor(employment_occupation),
    )
```

```{r}
str(train_all$h1n1_vaccine)

percent_h1n1 <- train_all %>% 
  tabyl(h1n1_vaccine)
percent_h1n1

percent_h1n1 %>%
  ggplot() +
  geom_col(aes(y = n, x = h1n1_vaccine)) +
  labs(x = "Received vaccine? (0 = no, 1 = yes)", 
       y = "Number of survey participants", 
       title = "Did survey participants get their H1N1 vaccine in 2009?")

str(train_all$seasonal_vaccine)

percent_seasonal <- train_all %>% 
  tabyl(seasonal_vaccine)
percent_seasonal

percent_seasonal%>%
  ggplot() +
  geom_col(aes(y = n, x = seasonal_vaccine)) +
  labs(x = "Received vaccine? (0 = no, 1 = yes)", 
       y = "Number of survey participants", 
       title = "Did survey participants get their seasonal vaccine in 2009?")
```

There are no missing values for the variables indicating whether the survey participants received their seasonal and/or H1N1 vaccination. Overall, 46.6% of survey participants got their seasonal vaccination while 21.2% got their H1N1 vaccination in 2009.

### Looking at all variables

```{r}
train_all %>%
  ggplot(mapping = aes(y = h1n1_concern, fill = h1n1_vaccine)) +
  geom_bar(position = "fill") +
  labs(x = "% participants", 
       y = "H1N1 concern level") +
       theme(legend.position = "bottom") -> A

train_all %>%
  ggplot(mapping = aes(y = h1n1_concern, fill = seasonal_vaccine)) +
  geom_bar(position = "fill") +
  labs(x = "% participants", 
       y = "Seasonal flu concern level") +
       theme(legend.position = "bottom") -> B

prow <- plot_grid(
  A, B,
  align = 'vh',
  hjust = -1,
  nrow = 1
)

plot_grid(prow, rel_widths = c(3, .4))
```

```{r, echo=FALSE}
train_all %>%
  ggplot(mapping = aes(y = h1n1_knowledge, fill = h1n1_vaccine)) +
  geom_bar(position = "fill") +
  labs(x = "% participants", 
       y = "H1N1 knowledge level") +
       theme(legend.position = "bottom") -> A

train_all %>%
  ggplot(mapping = aes(y = h1n1_knowledge, fill = seasonal_vaccine)) +
  geom_bar(position = "fill") +
  labs(x = "% participants", 
       y = "Seasonal flu knowledge level") +
       theme(legend.position = "bottom") -> B

prow <- plot_grid(
  A, B,
  align = 'vh',
  hjust = -1,
  nrow = 1
)

plot_grid(prow, rel_widths = c(3, .4))
```

```{r, echo=FALSE}
train_all %>%
  ggplot(mapping = aes(y = behavioral_antiviral_meds, fill = h1n1_vaccine)) +
  geom_bar(position = "fill") +
  labs(x = "% participants", 
       y = "Took antiviral medications") +
       theme(legend.position = "bottom") -> A

train_all %>%
  ggplot(mapping = aes(y = behavioral_antiviral_meds, fill = seasonal_vaccine)) +
  geom_bar(position = "fill") +
  labs(x = "% participants", 
       y = "Took antiviral medications") +
       theme(legend.position = "bottom") -> B

prow <- plot_grid(
  A, B,
  align = 'vh',
  hjust = -1,
  nrow = 1
)

plot_grid(prow, rel_widths = c(3, .4))
```

```{r, echo=FALSE}
train_all %>%
  ggplot(mapping = aes(y = behavioral_avoidance, fill = h1n1_vaccine)) +
  geom_bar(position = "fill") +
  labs(x = "% participants", 
       y = "Avoided people with flu") +
       theme(legend.position = "bottom") -> A

train_all %>%
  ggplot(mapping = aes(y = behavioral_avoidance, fill = seasonal_vaccine)) +
  geom_bar(position = "fill") +
  labs(x = "% participants", 
       y = "Avoided people with flu") +
       theme(legend.position = "bottom") -> B

prow <- plot_grid(
  A, B,
  align = 'vh',
  hjust = -1,
  nrow = 1
)

plot_grid(prow, rel_widths = c(3, .4))
```

```{r, echo=FALSE}
train_all %>%
  ggplot(mapping = aes(y = behavioral_face_mask, fill = h1n1_vaccine)) +
  geom_bar(position = "fill") +
  labs(x = "% participants", 
       y = "Bought a face mask") +
       theme(legend.position = "bottom") -> A

train_all %>%
  ggplot(mapping = aes(y = behavioral_face_mask, fill = seasonal_vaccine)) +
  geom_bar(position = "fill") +
  labs(x = "% participants", 
       y = "Bought a face mask") +
       theme(legend.position = "bottom") -> B

prow <- plot_grid(
  A, B,
  align = 'vh',
  hjust = -1,
  nrow = 1
)

plot_grid(prow, rel_widths = c(3, .4))
```

```{r, echo=FALSE}
train_all %>%
  ggplot(mapping = aes(y = behavioral_wash_hands, fill = h1n1_vaccine)) +
  geom_bar(position = "fill") +
  labs(x = "% participants", 
       y = "Frequently washed hands") +
       theme(legend.position = "bottom") -> A

train_all %>%
  ggplot(mapping = aes(y = behavioral_wash_hands, fill = seasonal_vaccine)) +
  geom_bar(position = "fill") +
  labs(x = "% participants", 
       y = "Frequently washed hands") +
       theme(legend.position = "bottom") -> B

prow <- plot_grid(
  A, B,
  align = 'vh',
  hjust = -1,
  nrow = 1
)

plot_grid(prow, rel_widths = c(3, .4))
```

```{r, echo=FALSE}
train_all %>%
  ggplot(mapping = aes(y = behavioral_large_gatherings, fill = h1n1_vaccine)) +
  geom_bar(position = "fill") +
  labs(x = "% participants", 
       y = "Reduced time at large gatherings") +
       theme(legend.position = "bottom") -> A

train_all %>%
  ggplot(mapping = aes(y = behavioral_large_gatherings, fill = seasonal_vaccine)) +
  geom_bar(position = "fill") +
  labs(x = "% participants", 
       y = "Reduced time at large gatherings") +
       theme(legend.position = "bottom") -> B

prow <- plot_grid(
  A, B,
  align = 'vh',
  hjust = -1,
  nrow = 1
)

plot_grid(prow, rel_widths = c(3, .4))
```

```{r, echo=FALSE}
train_all %>%
  ggplot(mapping = aes(y = behavioral_outside_home, fill = h1n1_vaccine)) +
  geom_bar(position = "fill") +
  labs(x = "% participants", 
       y = "Reduced time with people outside household") +
       theme(legend.position = "bottom") -> A

train_all %>%
  ggplot(mapping = aes(y = behavioral_outside_home, fill = seasonal_vaccine)) +
  geom_bar(position = "fill") +
  labs(x = "% participants", 
       y = "Reduced time with people outside household") +
       theme(legend.position = "bottom") -> B

prow <- plot_grid(
  A, B,
  align = 'vh',
  hjust = -1,
  nrow = 1
)

plot_grid(prow, rel_widths = c(3, .4))
```

```{r, echo=FALSE}
train_all %>%
  ggplot(mapping = aes(y = behavioral_touch_face, fill = h1n1_vaccine)) +
  geom_bar(position = "fill") +
  labs(x = "% participants", 
       y = "Avoided touching face") +
       theme(legend.position = "bottom") -> A

train_all %>%
  ggplot(mapping = aes(y = behavioral_touch_face, fill = seasonal_vaccine)) +
  geom_bar(position = "fill") +
  labs(x = "% participants", 
       y = "Avoided touching face") +
       theme(legend.position = "bottom") -> B

prow <- plot_grid(
  A, B,
  align = 'vh',
  hjust = -1,
  nrow = 1
)

plot_grid(prow, rel_widths = c(3, .4))
```

```{r, echo=FALSE}
train_all %>%
  ggplot(mapping = aes(y = doctor_recc_h1n1, fill = h1n1_vaccine)) +
  geom_bar(position = "fill") +
  labs(x = "% participants", 
       y = "H1N1 vaccine was recommended by doctor") +
       theme(legend.position = "bottom") -> A

train_all %>%
  ggplot(mapping = aes(y = doctor_recc_h1n1, fill = seasonal_vaccine)) +
  geom_bar(position = "fill") +
  labs(x = "% participants", 
       y = "H1N1 vaccine was recommended by doctor") +
       theme(legend.position = "bottom") -> B

prow <- plot_grid(
  A, B,
  align = 'vh',
  hjust = -1,
  nrow = 1
)

plot_grid(prow, rel_widths = c(3, .4))
```

```{r, echo=FALSE}
train_all %>%
  ggplot(mapping = aes(y = doctor_recc_seasonal, fill = h1n1_vaccine)) +
  geom_bar(position = "fill") +
  labs(x = "% participants", 
       y = "Seasonal vaccine was recommended by doctor") +
       theme(legend.position = "bottom") -> A

train_all %>%
  ggplot(mapping = aes(y = doctor_recc_seasonal, fill = seasonal_vaccine)) +
  geom_bar(position = "fill") +
  labs(x = "% participants", 
       y = "Seasonal vaccine was recommended by doctor") +
       theme(legend.position = "bottom") -> B

prow <- plot_grid(
  A, B,
  align = 'vh',
  hjust = -1,
  nrow = 1
)

plot_grid(prow, rel_widths = c(3, .4))
```

```{r, echo=FALSE}
train_all %>%
  ggplot(mapping = aes(y = chronic_med_condition, fill = h1n1_vaccine)) +
  geom_bar(position = "fill") +
  labs(x = "% participants", 
       y = "Has a chronic medical condition") +
       theme(legend.position = "bottom") -> A

train_all %>%
  ggplot(mapping = aes(y = chronic_med_condition, fill = seasonal_vaccine)) +
  geom_bar(position = "fill") +
  labs(x = "% participants", 
       y = "Has a chronic medical condition") +
       theme(legend.position = "bottom") -> B

prow <- plot_grid(
  A, B,
  align = 'vh',
  hjust = -1,
  nrow = 1
)

plot_grid(prow, rel_widths = c(3, .4))
```

```{r, echo=FALSE}
train_all %>%
  ggplot(mapping = aes(y = child_under_6_months, fill = h1n1_vaccine)) +
  geom_bar(position = "fill") +
  labs(x = "% participants", 
       y = "Has regular close contact wiht baby") +
       theme(legend.position = "bottom") -> A

train_all %>%
  ggplot(mapping = aes(y = child_under_6_months, fill = seasonal_vaccine)) +
  geom_bar(position = "fill") +
  labs(x = "% participants", 
       y = "Has regular close contact wiht baby") +
       theme(legend.position = "bottom") -> B

prow <- plot_grid(
  A, B,
  align = 'vh',
  hjust = -1,
  nrow = 1
)

plot_grid(prow, rel_widths = c(3, .4))
```

```{r, echo=FALSE}
train_all %>%
  ggplot(mapping = aes(y = health_worker, fill = h1n1_vaccine)) +
  geom_bar(position = "fill") +
  labs(x = "% participants", 
       y = "Is a health worker") +
       theme(legend.position = "bottom") -> A

train_all %>%
  ggplot(mapping = aes(y = health_worker, fill = seasonal_vaccine)) +
  geom_bar(position = "fill") +
  labs(x = "% participants", 
       y = "Is a health worker") +
       theme(legend.position = "bottom") -> B

prow <- plot_grid(
  A, B,
  align = 'vh',
  hjust = -1,
  nrow = 1
)

plot_grid(prow, rel_widths = c(3, .4))
```

```{r, echo=FALSE}
train_all %>%
  ggplot(mapping = aes(y = health_insurance, fill = h1n1_vaccine)) +
  geom_bar(position = "fill") +
  labs(x = "% participants", 
       y = "Has health insurance") +
       theme(legend.position = "bottom") -> A

train_all %>%
  ggplot(mapping = aes(y = health_insurance, fill = seasonal_vaccine)) +
  geom_bar(position = "fill") +
  labs(x = "% participants", 
       y = "Has health insurance") +
       theme(legend.position = "bottom") -> B

prow <- plot_grid(
  A, B,
  align = 'vh',
  hjust = -1,
  nrow = 1
)

plot_grid(prow, rel_widths = c(3, .4))
```

```{r, echo=FALSE}
train_all %>%
  ggplot(mapping = aes(y = opinion_h1n1_vacc_effective, fill = h1n1_vaccine)) +
  geom_bar(position = "fill") +
  labs(x = "% participants", 
       y = "Thinks H1N1 vaccine is effective") +
       theme(legend.position = "bottom") -> A

train_all %>%
  ggplot(mapping = aes(y = opinion_h1n1_vacc_effective, fill = seasonal_vaccine)) +
  geom_bar(position = "fill") +
  labs(x = "% participants", 
       y = "Thinks H1N1 vaccine is effective") +
       theme(legend.position = "bottom") -> B

prow <- plot_grid(
  A, B,
  align = 'vh',
  hjust = -1,
  nrow = 1
)

plot_grid(prow, rel_widths = c(3, .4))
```

```{r, echo=FALSE}
train_all %>%
  ggplot(mapping = aes(y = opinion_h1n1_risk, fill = h1n1_vaccine)) +
  geom_bar(position = "fill") +
  labs(x = "% participants", 
       y = "Risk of getting sick without H1N1 vaccine") +
       theme(legend.position = "bottom") -> A

train_all %>%
  ggplot(mapping = aes(y = opinion_h1n1_risk, fill = seasonal_vaccine)) +
  geom_bar(position = "fill") +
  labs(x = "% participants", 
       y = "Risk of getting sick without H1N1 vaccine") +
       theme(legend.position = "bottom") -> B

prow <- plot_grid(
  A, B,
  align = 'vh',
  hjust = -1,
  nrow = 1
)

plot_grid(prow, rel_widths = c(3, .4))
```

```{r, echo=FALSE}
train_all %>%
  ggplot(mapping = aes(y = opinion_h1n1_sick_from_vacc, fill = h1n1_vaccine)) +
  geom_bar(position = "fill") +
  labs(x = "% participants", 
       y = "Worry of getting sick from taking H1N1 vaccine") +
       theme(legend.position = "bottom") -> A

train_all %>%
  ggplot(mapping = aes(y = opinion_h1n1_sick_from_vacc, fill = seasonal_vaccine)) +
  geom_bar(position = "fill") +
  labs(x = "% participants", 
       y = "Worry of getting sick from taking H1N1 vaccine") +
       theme(legend.position = "bottom") -> B

prow <- plot_grid(
  A, B,
  align = 'vh',
  hjust = -1,
  nrow = 1
)

plot_grid(prow, rel_widths = c(3, .4))
```


```{r, echo=FALSE}
train_all %>%
  ggplot(mapping = aes(y = opinion_seas_vacc_effective, fill = h1n1_vaccine)) +
  geom_bar(position = "fill") +
  labs(x = "% participants", 
       y = "Thinks seasonal vaccine is effective") +
       theme(legend.position = "bottom") -> A

train_all %>%
  ggplot(mapping = aes(y = opinion_seas_vacc_effective, fill = seasonal_vaccine)) +
  geom_bar(position = "fill") +
  labs(x = "% participants", 
       y = "Thinks seasonal vaccine is effective") +
       theme(legend.position = "bottom") -> B

prow <- plot_grid(
  A, B,
  align = 'vh',
  hjust = -1,
  nrow = 1
)

plot_grid(prow, rel_widths = c(3, .4))
```

```{r, echo=FALSE}
train_all %>%
  ggplot(mapping = aes(y = opinion_seas_risk, fill = h1n1_vaccine)) +
  geom_bar(position = "fill") +
  labs(x = "% participants", 
       y = "Risk of getting sick without seasonal vaccine") +
       theme(legend.position = "bottom") -> A

train_all %>%
  ggplot(mapping = aes(y = opinion_seas_risk, fill = seasonal_vaccine)) +
  geom_bar(position = "fill") +
  labs(x = "% participants", 
       y = "Risk of getting sick without seasonal vaccine") +
       theme(legend.position = "bottom") -> B

prow <- plot_grid(
  A, B,
  align = 'vh',
  hjust = -1,
  nrow = 1
)

plot_grid(prow, rel_widths = c(3, .4))
```

```{r, echo=FALSE}
train_all %>%
  ggplot(mapping = aes(y = opinion_seas_sick_from_vacc, fill = h1n1_vaccine)) +
  geom_bar(position = "fill") +
  labs(x = "% participants", 
       y = "Worry of getting sick from taking seasonal vaccine") +
       theme(legend.position = "bottom") -> A

train_all %>%
  ggplot(mapping = aes(y = opinion_seas_sick_from_vacc, fill = seasonal_vaccine)) +
  geom_bar(position = "fill") +
  labs(x = "% participants", 
       y = "Worry of getting sick from taking seasonal vaccine") +
       theme(legend.position = "bottom") -> B

prow <- plot_grid(
  A, B,
  align = 'vh',
  hjust = -1,
  nrow = 1
)

plot_grid(prow, rel_widths = c(3, .4))
```

```{r, echo=FALSE}
train_all %>%
  ggplot(mapping = aes(y = age_group, fill = h1n1_vaccine)) +
  geom_bar(position = "fill") +
  labs(x = "% participants", 
       y = "Age group") +
       theme(legend.position = "bottom") -> A

train_all %>%
  ggplot(mapping = aes(y = age_group, fill = seasonal_vaccine)) +
  geom_bar(position = "fill") +
  labs(x = "% participants", 
       y = "Age group") +
       theme(legend.position = "bottom") -> B

prow <- plot_grid(
  A, B,
  align = 'vh',
  hjust = -1,
  nrow = 1
)

plot_grid(prow, rel_widths = c(3, .4))
```

```{r, echo=FALSE}
train_all %>%
  ggplot(mapping = aes(y = education, fill = h1n1_vaccine)) +
  geom_bar(position = "fill") +
  labs(x = "% participants", 
       y = "Age group") +
       theme(legend.position = "bottom") -> A

train_all %>%
  ggplot(mapping = aes(y = education, fill = seasonal_vaccine)) +
  geom_bar(position = "fill") +
  labs(x = "% participants", 
       y = "Age group") +
       theme(legend.position = "bottom") -> B

prow <- plot_grid(
  A, B,
  align = 'vh',
  hjust = -1,
  nrow = 1
)

plot_grid(prow, rel_widths = c(3, .4))
```

```{r, echo=FALSE}
train_all %>%
  ggplot(mapping = aes(y = race, fill = h1n1_vaccine)) +
  geom_bar(position = "fill") +
  labs(x = "% participants", 
       y = "Race") +
       theme(legend.position = "bottom") -> A

train_all %>%
  ggplot(mapping = aes(y = race, fill = seasonal_vaccine)) +
  geom_bar(position = "fill") +
  labs(x = "% participants", 
       y = "Race") +
       theme(legend.position = "bottom") -> B

prow <- plot_grid(
  A, B,
  align = 'vh',
  hjust = -1,
  nrow = 1
)

plot_grid(prow, rel_widths = c(3, .4))
```

```{r, echo=FALSE}
train_all %>%
  ggplot(mapping = aes(y = sex, fill = h1n1_vaccine)) +
  geom_bar(position = "fill") +
  labs(x = "% participants", 
       y = "Sex") +
       theme(legend.position = "bottom") -> A

train_all %>%
  ggplot(mapping = aes(y = sex, fill = seasonal_vaccine)) +
  geom_bar(position = "fill") +
  labs(x = "% participants", 
       y = "Sex") +
       theme(legend.position = "bottom") -> B

prow <- plot_grid(
  A, B,
  align = 'vh',
  hjust = -1,
  nrow = 1
)

plot_grid(prow, rel_widths = c(3, .4))
```

```{r, echo=FALSE}
train_all %>%
  ggplot(mapping = aes(y = income_poverty, fill = h1n1_vaccine)) +
  geom_bar(position = "fill") +
  labs(x = "% participants", 
       y = "Income") +
       theme(legend.position = "bottom") -> A

train_all %>%
  ggplot(mapping = aes(y = income_poverty, fill = seasonal_vaccine)) +
  geom_bar(position = "fill") +
  labs(x = "% participants", 
       y = "Income") +
       theme(legend.position = "bottom") -> B

prow <- plot_grid(
  A, B,
  align = 'vh',
  hjust = -1,
  nrow = 1
)

plot_grid(prow, rel_widths = c(3, .4))
```

```{r, echo=FALSE}
train_all %>%
  ggplot(mapping = aes(y = marital_status, fill = h1n1_vaccine)) +
  geom_bar(position = "fill") +
  labs(x = "% participants", 
       y = "Marital status") +
       theme(legend.position = "bottom") -> A

train_all %>%
  ggplot(mapping = aes(y = marital_status, fill = seasonal_vaccine)) +
  geom_bar(position = "fill") +
  labs(x = "% participants", 
       y = "Marital status") +
       theme(legend.position = "bottom") -> B

prow <- plot_grid(
  A, B,
  align = 'vh',
  hjust = -1,
  nrow = 1
)

plot_grid(prow, rel_widths = c(3, .4))
```

```{r, echo=FALSE}
train_all %>%
  ggplot(mapping = aes(y = rent_or_own, fill = h1n1_vaccine)) +
  geom_bar(position = "fill") +
  labs(x = "% participants", 
       y = "Rent or own") +
       theme(legend.position = "bottom") -> A

train_all %>%
  ggplot(mapping = aes(y = rent_or_own, fill = seasonal_vaccine)) +
  geom_bar(position = "fill") +
  labs(x = "% participants", 
       y = "Rent or own") +
       theme(legend.position = "bottom") -> B

prow <- plot_grid(
  A, B,
  align = 'vh',
  hjust = -1,
  nrow = 1
)

plot_grid(prow, rel_widths = c(3, .4))
```

```{r, echo=FALSE}
train_all %>%
  ggplot(mapping = aes(y = employment_status, fill = h1n1_vaccine)) +
  geom_bar(position = "fill") +
  labs(x = "% participants", 
       y = "Employment status") +
       theme(legend.position = "bottom") -> A

train_all %>%
  ggplot(mapping = aes(y = employment_status, fill = seasonal_vaccine)) +
  geom_bar(position = "fill") +
  labs(x = "% participants", 
       y = "Employment status") +
       theme(legend.position = "bottom") -> B

prow <- plot_grid(
  A, B,
  align = 'vh',
  hjust = -1,
  nrow = 1
)

plot_grid(prow, rel_widths = c(3, .4))
```

```{r, echo=FALSE}
train_all %>%
  ggplot(mapping = aes(y = hhs_geo_region, fill = h1n1_vaccine)) +
  geom_bar(position = "fill") +
  labs(x = "% participants", 
       y = "Geographic classification of residence") +
       theme(legend.position = "bottom") -> A

train_all %>%
  ggplot(mapping = aes(y = hhs_geo_region, fill = seasonal_vaccine)) +
  geom_bar(position = "fill") +
  labs(x = "% participants", 
       y = "Geographic classification of residence") +
       theme(legend.position = "bottom") -> B

prow <- plot_grid(
  A, B,
  align = 'vh',
  hjust = -1,
  nrow = 1
)

plot_grid(prow, rel_widths = c(3, .4))
```

```{r, echo=FALSE}
train_all %>%
  ggplot(mapping = aes(y = census_msa, fill = h1n1_vaccine)) +
  geom_bar(position = "fill") +
  labs(x = "% participants", 
       y = "Residence in metropolitan area") +
       theme(legend.position = "bottom") -> A

train_all %>%
  ggplot(mapping = aes(y = census_msa, fill = seasonal_vaccine)) +
  geom_bar(position = "fill") +
  labs(x = "% participants", 
       y = "Residence in metropolitan area") +
       theme(legend.position = "bottom") -> B

prow <- plot_grid(
  A, B,
  align = 'vh',
  hjust = -1,
  nrow = 1
)

plot_grid(prow, rel_widths = c(3, .4))
```

```{r, echo=FALSE}
train_all %>%
  ggplot(mapping = aes(y = household_adults, fill = h1n1_vaccine)) +
  geom_bar(position = "fill") +
  labs(x = "% participants", 
       y = "Number of other adults in household") +
       theme(legend.position = "bottom") -> A

train_all %>%
  ggplot(mapping = aes(y = household_adults, fill = seasonal_vaccine)) +
  geom_bar(position = "fill") +
  labs(x = "% participants", 
       y = "Number of other adults in household") +
       theme(legend.position = "bottom") -> B

prow <- plot_grid(
  A, B,
  align = 'vh',
  hjust = -1,
  nrow = 1
)

plot_grid(prow, rel_widths = c(3, .4))
```

```{r, echo=FALSE}
train_all %>%
  ggplot(mapping = aes(y = household_children, fill = h1n1_vaccine)) +
  geom_bar(position = "fill") +
  labs(x = "% participants", 
       y = "Number of children in household") +
       theme(legend.position = "bottom") -> A

train_all %>%
  ggplot(mapping = aes(y = household_children, fill = seasonal_vaccine)) +
  geom_bar(position = "fill") +
  labs(x = "% participants", 
       y = "Number of children in household") +
       theme(legend.position = "bottom") -> B

prow <- plot_grid(
  A, B,
  align = 'vh',
  hjust = -1,
  nrow = 1
)

plot_grid(prow, rel_widths = c(3, .4))
```

```{r, echo=FALSE}
train_all %>%
  ggplot(mapping = aes(y = employment_industry, fill = h1n1_vaccine)) +
  geom_bar(position = "fill") +
  labs(x = "% participants", 
       y = "Industry of employment") +
       theme(legend.position = "bottom") -> A

train_all %>%
  ggplot(mapping = aes(y = employment_industry, fill = seasonal_vaccine)) +
  geom_bar(position = "fill") +
  labs(x = "% participants", 
       y = "Industry of employment") +
       theme(legend.position = "bottom") -> B

prow <- plot_grid(
  A, B,
  align = 'vh',
  hjust = -1,
  nrow = 1
)

plot_grid(prow, rel_widths = c(3, .4))
```

```{r, echo=FALSE}
train_all %>%
  ggplot(mapping = aes(y = employment_occupation, fill = h1n1_vaccine)) +
  geom_bar(position = "fill") +
  labs(x = "% participants", 
       y = "Occupation") +
       theme(legend.position = "bottom") -> A

train_all %>%
  ggplot(mapping = aes(y = employment_occupation, fill = seasonal_vaccine)) +
  geom_bar(position = "fill") +
  labs(x = "% participants", 
       y = "Occupation") +
       theme(legend.position = "bottom") -> B

prow <- plot_grid(
  A, B,
  align = 'vh',
  hjust = -1,
  nrow = 1
)

plot_grid(prow, rel_widths = c(3, .4))
```

## TRYING TO CREATE PLOTS WITH A LOOP

# ```{r}
# all_variables <- names(train_all)[4:38]
# 
# for (variable in all_variables) {
#   A <- train_all %>%
#     ggplot(mapping = aes(y = variable, fill = h1n1_vaccine)) +
#     geom_bar(position = "fill") +
#     labs(x = "% participants") + 
#     #       y = "Occupation") +
#     theme(legend.position = "bottom")
#   
#   B <- train_all %>% 
#     ggplot(mapping = aes(y = variable, fill = seasonal_vaccine)) +
#     geom_bar(position = "fill") +
#     labs(x = "% participants") + 
#     #       y = "Occupation") +
#     theme(legend.position = "bottom")
#   
#   prow <- plot_grid(
#     A, B,
#     align = 'vh',
#     hjust = -1,
#     nrow = 1
#   )
#   
#   plot_grid(prow, rel_widths = c(3, .4))
# }
# ```

### Missing values

We should acknowledge that the above visualisations we done using the raw data. One could be interested in the number of missing values for each variable in the dataset. First, in the train set:

```{r}
na_count <- sapply(train_all, function(y) sum(length(which(is.na(y)))))
na_count <- data.frame(na_count)
na_count <- na_count %>%
  add_column(percent_missing = na_count$na_count/26707*100)
na_count
```

And then, in the test dataset for which we have to predict the labels:

```{r}
na_count <- sapply(test_features, function(y) sum(length(which(is.na(y)))))
na_count <- data.frame(na_count)
na_count <- na_count %>%
  add_column(percent_missing = na_count$na_count/26708*100)
na_count
```

The respondant_id variable is common to both datasets (training and testing) and has no missing values. The two variables only found in the training dataset, the h1n1_vaccine and the seasonal_vaccine variables, also have no NAs. For the remaining of the variables, we see that trends in missing values seem to be the same in the training and the testing datasets. In both cases, the employment variables (industry and occupation) are missing for approximately 50% of respondants; the health_insurance variable is missing for approximately 46% of respondants; the income variable is missing for almost 17% of respondants; whether the H1N1 or the seasonal vaccines had been recommended by their doctors is missing for 8% of respondants; and whether the respondant owns or rents is missing for almost 8% of respondants. Finally, education, marital status and employment status are also missing for approximately 5% of respondants.

## NEXT STEPS

The next step is to build a model that, based on survey answers, will predict the float probabilities (ranging between 0.0 and 1.0) of each participant to have taken the H1N1 and/or the seasonal flu shot(s), or in other words the probabilities that a person received each vaccine. As this is a multilabel problem, the submission file should include a probability for each vaccine.

### What is a multilabel problem?

Based on the [scikit learn website](https://scikit-learn.org/stable/modules/multiclass.html), **multilabel classification** assigns to each sample a set of target labels so predicting properties of a data-point that are not mutually exclusive. For example, a text might be about any of religion, politics, finance or education at the same time or none of these. On the opposite, **multiclass classification** means a classification task with more than two classes; e.g., classify a set of images of fruits which may be oranges, apples, or pears. Multiclass classification makes the assumption that each sample is assigned to one and only one label: a fruit can be either an apple or a pear but not both at the same time.

OK, so we have several binary and categorical variables to model probabilities of vaccination.


<!-- All variables -->

<!-- h1n1_concern -->
<!-- h1n1_knowledge -->
<!-- behavioral_antiviral_meds -->
<!-- behavioral_avoidance -->
<!-- behavioral_face_mask -->
<!-- behavioral_wash_hands -->
<!-- behavioral_large_gatherings -->
<!-- behavioral_outside_home -->
<!-- behavioral_touch_face -->
<!-- doctor_recc_h1n1 -->
<!-- doctor_recc_seasonal -->
<!-- chronic_med_condition -->
<!-- child_under_6_months -->
<!-- health_worker -->
<!-- health_insurance -->
<!-- opinion_h1n1_vacc_effective -->
<!-- opinion_h1n1_risk -->
<!-- opinion_h1n1_sick_from_vacc -->
<!-- opinion_seas_vacc_effective -->
<!-- opinion_seas_risk -->
<!-- opinion_seas_sick_from_vacc -->
<!-- age_group -->
<!-- education -->
<!-- race -->
<!-- sex -->
<!-- income_poverty -->
<!-- marital_status -->
<!-- rent_or_own -->
<!-- employment_status -->
<!-- hhs_geo_region -->
<!-- census_msa -->
<!-- household_adults -->
<!-- household_children -->
<!-- employment_industry -->
<!-- employment_occupation -->